% ACRONYMS & GLOSSARY

\section{C.1 ACRONYMS}

% TABLE ROW: | Acronym | Definition |
% TABLE ROW: |---------|------------|
% TABLE ROW: | **RCWS** | Remote Controlled Weapon Station |
% TABLE ROW: | **DCU** | Display and Control Unit |
% TABLE ROW: | **LRF** | Laser Range Finder |
% TABLE ROW: | **IMU** | Inertial Measurement Unit |
% TABLE ROW: | **AHRS** | Attitude and Heading Reference System |
% TABLE ROW: | **FOV** | Field of View |
% TABLE ROW: | **HFOV** | Horizontal Field of View |
% TABLE ROW: | **VFOV** | Vertical Field of View |
% TABLE ROW: | **LAC** | Lead Angle Compensation |
% TABLE ROW: | **CCIP** | Continuously Computed Impact Point |
% TABLE ROW: | **TRP** | Target Reference Point |
% TABLE ROW: | **PID** | Positive Identification |
% TABLE ROW: | **ROE** | Rules of Engagement |
% TABLE ROW: | **BDA** | Battle Damage Assessment |
% TABLE ROW: | **TOF** | Time of Flight |
% TABLE ROW: | **LUT** | Look-Up Table (Thermal) |
% TABLE ROW: | **FFC** | Flat Field Correction (Thermal camera calibration) |
% TABLE ROW: | **E-Stop** | Emergency Stop |
% TABLE ROW: | **OSD** | On-Screen Display |

\section{C.2 GLOSSARY}

\textbf{Acquisition}: The phase where operator positions and sizes the tracking gate over the target before requesting lock-on.

\textbf{Azimuth}: Horizontal angle, measured in degrees (0-360\degree{}). 0\degree{}=North, 90\degree{}=East, 180\degree{}=South, 270\degree{}=West.

\textbf{Boresight}: The alignment between the camera line-of-sight and the weapon bore axis. Zeroing corrects boresight offset.

\textbf{Coast Mode}: Tracking phase where the target is temporarily lost and the system predicts target position to maintain track.

\textbf{Dead Man Switch}: Safety interlock requiring continuous operator pressure to enable certain functions (LAC activation).

\textbf{Elevation}: Vertical angle, measured in degrees. 0\degree{}=horizon, +90\degree{}=zenith, -90\degree{}=nadir.

\textbf{Gimbal}: The stabilized platform that holds the camera and weapon, allowing azimuth and elevation motion.

\textbf{Lead Angle}: The angular offset between a moving target's current position and the predicted intercept point, compensating for projectile time-of-flight.

\textbf{Lock Pending}: Tracking phase where the system is initializing the tracker algorithm on the target.

\textbf{Reticle}: The aiming point displayed on the video feed, showing where the weapon will impact (with zeroing/ballistics applied).

\textbf{Stabilization}: The system's ability to compensate for platform motion (vehicle movement, ship roll/pitch) to keep the gimbal pointed at the target.

\textbf{Zeroing}: The process of correcting the offset between the camera aim point and weapon impact point, ensuring the reticle accurately represents where rounds will hit.
